### 2021-04-09 Chapter-2/Chapter-2.tex
Updates from Overleaf

>>>>

\section{Trace-based Binary Analysis}
Trace-based binary analysis can be seen as a type of dynamic analysis. It 
analyzes one concrete program path one time rather than trying to cover
as many paths as possible. Compared to static analysis, trace-based analysis
is usually more precise as it can use runtime information. It usually has
two steps. The first step is collecting trace information. Existing
approaches usually often rely on binary instrumentation frameworks or emulators (e.g, Intel Pin~\cite{luk2005pin},
Valgrind~\cite{nethercote2007valgrind}, QEMU). The second step is analyzing the trace using techniques, such
as symbolic execution, taint analysis. Depending on when the analysis is launched,
there are two kinds of trace-based analysis, online analysis and offline analysis.
As the name suggests, online analysis is performed at runtime. The target program's
data can be modified directly in memory, which is useful in fuzzing because the analysis
can force the program to go through into a specific branch. Contrary to online analysis,
offline analysis or post analysis happens when the program finish executions. 
Trace-based binary analysis has been adopted in several tasks like algorithm
detection, vulnerability detection and malware analysis. We only mention a few of
most related works here. Xu et al.~\cite{xu2017cryptographic} introduce bit-wise symbolic execution, which can
identify crypto algorithms in obfuscated binaries. Ming et al.~\cite{ming2017binsim} use 
system call sliced segment equivalence checking to do binary diffing. Jia et al.~\cite{jia2017towards}
perform an offline analysis on execution traces to identify heap overflows.

There are several known binary analysis frameworks that can ease users 
to launch analysis on binary executable. BitBlaze~\cite{brumley2011bap} is a binary analysis platform
that provides both the static and dynamic analysis. It uses tracecap plugin to 
collect execution trace and convert the trace into Vine IR. Binary Analysis Platform (BAP)
is an another binary analysis platform. Similar to BitBlaze, it use a Pintrace tool to
collect execution trace and convert the trace into BAP IR. Angr~\cite{shoshitaishvili2016state}, the most popular
binary analysis platform recently, also support trace-based analysis. It first convert
each instruction into VEX IR and interpret each IR in Python.

Above existing well-known binary analysis frameworks all adopt the IR layer, which make
it easy to implement the framework and support multiple architectures. However, it can have
a very low efficiency and long traces. All IR must be interpreted no matter if symbolic variables
are involved or not. Besides, as side-channels are low level problems in general, the IR
design will also lose some information. For example, IR-level branches are not necessarily 
a super-set or a sub-set of machine-code level branches. Some IR-level branches can be compiled into
non-branch instructions like conditional moves. Those above limitations motivate us to
implement a new trace-based binary analysis framework.

### 2021-04-09 Chapter-5/Chapter-5.tex
Updates from Overleaf

\section{Background and Threat Model}
In the section, we first provide a brief introduction of the side-channel attacks that exploit the memory access patterns. After that, we give an overview of the background knowledge of information theory. Finally, we present the threat model of the paper.

@@

\section{Evaluation}

>>>>

\section{Background and Threat Model}
In the section, we give an overview of the background knowledge of information theory. Finally, we present the threat model of the paper.

@@

\section{Evaluation}
In this section, we evaluate \tool{} on several small benchmarks and real-world software trying to answer the following questions:

\begin{itemize}
\item \textbf{Effectiveness:} Can \tool{} quantify the information leakage with an conservative estimation? If so, what is loss compared it with the real leakage?
\item \textbf{Performance:} How much overhead can \tool{} produce?
\item \textbf{Usage:} What is the real usage of \tool{}? Can \tool{} handle both Cryptography and Non-cryptography libraries? Can \tool{} help developers find and fix side-channel leakages?
\end{itemize}

\textbf{Evaluation setup.} We run all the following experiment in a server machine with Ubuntu 18.04 LTS. The server machine equips with 2.90GHz Intel Xeon(R) E5-2690 CPU with 128GB RAM memory. We use the default compilation settings to build the source code of the software into ELF 64-bit executables with GCC 7.5. The server has many cores, but we do not use all cores during the evaluation. We sometimes run several experiments concurrently. The evaluation time presented in the following section is based on a single-core.

\begin{table*}[h]
\footnotesize
\caption{Evaluation results overview: Name, Side-channel Leaks\,(Leaks), Secret-dependent Control-flows\,(CF), Secret-dependent Data-flows\,(DA),The number of instructions\,(Program Size), Symbolic Execution\,(SE), and Monte Carlo\,(MC).}\label{table:over_result}
\begin{tabular}{lrrrrrrrrrrrr}\toprule

\textbf{Name}   & \multicolumn{2}{c}{\textbf{Input Data}} &  \multicolumn{3}{c}{\textbf{Output Leakage (bits)}} & \multicolumn{3}{c}{\textbf{Maximum Leakage (bits)}}   & \multicolumn{2}{c}{\textbf{Program Size}}    & \multicolumn{2}{c}{\textbf{Performance}}    \\ 
\cmidrule(lr){2-3}\cmidrule(lr){4-6}\cmidrule(lr){7-9}\cmidrule(lr){10-11}\cmidrule(lr){12-13}& \# & bits & Byte & Cache Line& Page & Byte & Cache Line& Page & LoC & Size & Fuzzing & Comparison
\\\midrule
AES       \\
AES       \\
AES \\
RC4 \\
RC4 \\
RC4 \\
RSA \\
RSA \\
Tiny DNN \\
GDK \\
Total             \\
\bottomrule
\end{tabular}

\end{table*}

\subsection{Overview}

\subsection{Benchmarks}
\subsubsection{Password Checker}

\subsubsection{Electronic Purse}

\subsubsection{Lookup Table}

\subsection{Cryptography Library}

\subsection{Case Study: Attacks on Multi-class Classification Inference Engine}
In the section, we demonstrate an attack that can recover the deep learning model inference output by the controlled-channel attack. Running the machine learning inference engine inside the enclave is a typical scenario for machine learning as service. The machine learning service provider upload the the trained model into an enclave running on the cloud platform and provide machine learning service to a third party user. With the help of the enclave, both the model and the user's inferred result is protected from the outside. However, we will show that the above information can be easily retrieved from the untrusted world through the side-channel attack.

We use MNIST as the dataset and LeNet-5 for MNIST digits recognition task. LeNet-5 is known to work well on handwritten digit recognition. We first train the network. The batch size in our experiment is 10 and the numbers of epochs is 30. After the training, the accuracy of the neural networks on test set images is 99.5\%.

Then we use the model to infer the images. During the inference, we also record the page access information.

\subsection{Case Study: Graphic Libraries}
